Differentially Private Bayesian Inference

### 2018-06-16 main.tex
update notes

\subsection{Accuracy Study Based on Hellinger Distance}
% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
%     \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
%   \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
%     \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
% \caption{The experimental results of accuracy of four algorithms}
% \label{fig_data}
% \end{center}
% \end{figure*}

@@

\bibliographystyle{plain}
\bibliography{bayesian.bib}

>>>>

\subsection{Accuracy Study Based on Hellinger Distance}
\label{subsec_accuracy_hellinger}
% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
%     \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
%   \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
%     \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
% \caption{The experimental results of accuracy of four algorithms}
% \label{fig_data}
% \end{center}
% \end{figure*}

@@

\subsection{Accuracy Study in Theory}
\label{subsec_accuracy_theory}
We studied the accuracy of our exponential mechanism and Laplace mechanism in theory. By computing the discrete probability of outputting each candidate in two mechanisms separately. We count the probabilities wrt. the steps from correct answer. For example, in the case where the correct posterior distribution is $\betad(5,5)$, the candidate $\betad(4,6)$ and $\betad(6,4)$ are of $1$ steps from $\betad(5,5)$; when correct posterior distribution is $\dirichlet(5,5,5)$, the candidate $\dirichlet(4,5,3)$, $\dirichlet(4,3,5)$, $\dirichlet(5,4,3)$, $\dirichlet(5,3,4)$, $\dirichlet(3,5,4)$ and $\dirichlet(5,5,5)$ are all of $1$ step from $\dirichlet(5,5,5)$. Under the Hellinger distance measurement, if two candidates are of the same steps from correct answer, they also have the same Hellinger distance from correct answer. i.e for every $\hlg(\bysinfer(x), z) = c$, it will have a corresponding steps $step(\hlg(\bysinfer(x), z) = c) = k$.

So in order to be more concise and comparable to the experiment results in Sec. \ref{subsec_accuracy_hellinger}, we sum up the probabilities values of candidates whose steps (i.e., the hellinger distance) from the correct answer are the same:
\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) = c] = \sum\limits_{\{z| \hlg(\bysinfer(x), z) = c\}}\frac{exp(\frac{- \epsilon c}{S(x)})}{NL_x}
\end{equation*}

Then we get groups of discrete probabilities wrt. the steps (i.e., Hellinegr distance) from the correct answer, and plot them. Under different settings, we got same results as in Fig. \ref{fig_theory_50_50}, \ref{fig_theory_20_20_20} and \ref{fig_theory_20_20_20_20}. The x-axis is the hellinger distance from correct answer, i.e. steps from correct answer. Since they have the same meaning, here we just use the hellinger distance to label the x-axis. The y-axis is the probability of output candidates with corresponding steps from correct answer.

\begin{figure*}
\begin{center}
\centering
  \subfigure[accuracy measurement based on Hellinger distance]{
    \includegraphics[width=0.48\textwidth]{theory_compare_50_50.eps}}
  \subfigure[discrete probabilities wrt. hellinger distance]{
    \includegraphics[width=0.48\textwidth]{50_50.eps}} 
\caption{Settings: Dirichlet prior distribution $\dirichlet(1,1)$, observed data $x = (49, 49) $,}
\label{fig_theory_50_50}
\end{center}
\end{figure*}

As shown in Fig. \ref{fig_theory_50_50}, our exponential mechanism is better than Laplace, both in experiments and in theory. In Fig. \ref{fig_theory_50_50} (a), the experiment results shown that the average accuracy of our mechanism is better than Laplace mechanism. In Our exponential mechanism can output good answer with higher probability and output bad answer with lower probability.

\begin{figure*}
\begin{center}
\centering
  \subfigure[accuracy measurement based on Hellinger distance]{
    \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20.eps}}
  \subfigure[discrete probabilities wrt. hellinger distance]{
    \includegraphics[width=0.48\textwidth]{20_20_20.eps}} 
\caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1)$, observed data $x = (20,20,20) $,}
\label{fig_theory_20_20_20}
\end{center}
\end{figure*}

In Fig. \ref{fig_theory_20_20_20}, we plotted these discrete probabilities under the case (x=(20,20,20)),  I think this plot shows the laplace mech performs better than ExpMech to some extent but not significant.

\begin{figure*}
\begin{center}
\centering
  \subfigure[accuracy measurement based on Hellinger distance]{
    \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20_20.eps}}
  \subfigure[discrete probabilities wrt. hellinger distance]{
    \includegraphics[width=0.48\textwidth]{20_20_20_20.eps}} 
\caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (20,20,20,20) $,}
\label{fig_theory_20_20_20_20}
\end{center}
\end{figure*}

In Fig. \ref{fig_theory_20_20_20_20}, we plotted these discrete probabilities under the case ($x=(20,20,20,20)$).  this plot can show clearly that the Laplace Mech are better than Exp Mech when the size is larger and order is higher.  The Laplace can output good answers with much higher probabilities, even though their performances on bad answers are not so obviously.
\bibliographystyle{plain}
\bibliography{bayesian.bib}
